A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-06 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Add network traffic growth citation

This increasingly dynamic environment for resources, particularly CPU,
must be coupled with a highly reliable system for data storage and a
suitable network infrastructure for delivering this data to where it
will be processed. While CPU and disk capacity is expected to increase
by respectively 15\% and 25\% per year for the same cost~\cite{CERN-COST-EST}, the trends of
research network capacity increases show a much steeper growth, such as
two orders of magnitude from now to HL-LHC times. Therefore, the
evolution of the computing models would need to be more network centric.

>>>>

This increasingly dynamic environment for resources, particularly CPU,
must be coupled with a highly reliable system for data storage and a
suitable network infrastructure for delivering this data to where it
will be processed. While CPU and disk capacity is expected to increase
by respectively 15\% and 25\% per year for the same cost~\cite{CERN-COST-EST}, the trends of
research network capacity increases show a much steeper growth, such as
two orders of magnitude from now to HL-LHC times~\cite{Roberts:17}. Therefore, the
evolution of the computing models would need to be more network centric.
